Reply to: 2022-05603 Intentional release of native species undermines ecological stability

### 2022-12-24 rmd/manuscript.Rmd
edit: grammar

The intentional release, however, can have wide-ranging consequences than previously thought, as the impacts can propagate through a diversity of ecological interactions [@careyNativeInvadersChallenges2012]. This recognition has sparked a discussion of how the massive introduction of native species alters short-term ecosystem dynamics [@hasegawaAreHatcheryChum2018; @nelsonEcologicalImplicationsChanging2019; @cucheroussetAreDomesticatedFreshwater2020]. Yet, current debates overlook the fact that we have rarely assessed the community-wide impact in the long-term. Ecological theory suggests that the stable coexistence of competing species through density-dependent feedback underpins the emergent stability of ecological communities [@tilmanEcologicalConsequencesChanges1999; @carrollNicheFitnessDifferences2011a; @loreauDoesFunctionalRedundancy2004]. Intentional release may disrupt the sensitive balance of species interactions because it introduces unnaturally high numbers of individuals into the wild [@laikreCompromisingGeneticDiversity2010; @careyNativeInvadersChallenges2012; @kitadaEconomicEcologicalGenetic2018]. Hence, this form of species management may intervene in the ecological process that allows competing species to coexist, ultimately degrading the long-term community stability. Evidence for this hypothesis is lacking, however.

@@

The intentional release had little or a stabilizing influence on community dynamics when carrying capacity was sufficiently large ($K=$ `r max(list_param[[2]]$k)`; **Figures S7 -- S10**). In particular, intentional release increased the enhanced species with a low population growth rate ($r_1=$ `r min(list_param[[2]]$r1)`; **Figure S7**), suggesting that weak intraspecific competition within the enhanced species (= $r_1 K^{-1}$) is needed for intentional release to be effective. The weak-competition scenario is likely in reintroduction of extirpated species or long-lived endangered species. In fact, some of the best evidence for successful intentional release comes from conservation programs of such species [@deguchiTranslocationHandrearingResult2017; @jonesRestorationMauritiusKestrel1995; @okahisaEvaluationOngoingCrested2022; @yackulicAssessingPopulationImpacts2021]. In the Sado island (Japan), for example, the once-extirpated Crested Ibis *Nipponia nippon* showed exponential growth of the population since the initial reintroduction of ten captive-bred individuals in 2008 [@okahisaEvaluationOngoingCrested2022]. Similarly, translocations of Humpback chub, a federally-listed fish species in the US, seem highly cost-effective in enhancing their tributary populations in the Little Colorado River [@yackulicAssessingPopulationImpacts2021]. However, the preponderance of unsuccessful reintroduction in conservation implies that the theoretical requirements for successful intentional release are not always met [@fischerAssessmentPublishedResults2000; @haagNorthAmericanFreshwater2012; @strayerEssayMakingMost2019]. Indeed, non-negligible numbers of projects seem to release captive-bred individuals into unsuitable habitats with compromised carrying capacities [@fischerAssessmentPublishedResults2000; @haagNorthAmericanFreshwater2012]. Our analysis suggests that such programs could rather impair biodiversity without noticeable demographic benefit to the enhanced species. Pre-release examination and restoration of environmental capacity may be key to successful release programs with minimal impacts on other community members.

@@

To demonstrate the relevance of our general theory to natural systems, we assessed the potential impacts of the intentional release of masu salmon (**Figure 1D**) on the long-term stability of stream fish communities in Hokkaido, Japan. In the protected watersheds (all separated by the ocean; **Figure 1C**), a long-term program exists to monitor stream fish communities along with the official release records. The release of masu salmon began in the 1950s; the release numbers vary due mainly to logistical reasons, while several of the watersheds are not subject to intentional release to preserve regional populations. This resulted in the average annual release ranging from `r round(min(df_stock_mu$mean_stock), 2)` (no release) to `r round(max(df_stock_mu$mean_stock), 2)` million fish across watersheds during 1999 -- 2019. The majority of release occurs in spring near fish survey locations, after which salmon fry stays in freshwater for at least one year with other stream fishes (see **Figure S16** for a co-occurrence matrix in our dataset). Therefore, the study system sets the stage for a "natural experiment" to test our theoretical predictions. We used the data from 1999 to 2019 at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` independent watersheds (see **Methods** for selection criteria). Using hierarchical Bayesian models, we quantified the effect of intentional release on community dynamics while accounting for the potential effects of climates and local abiotic factors.

@@

The reduced fitness of hatchery masu salmon may also play a role in the observed response. Like other salmonids, masu salmon exhibits a life history of "partial migration"; in our study region, the majority of individuals migrate to the ocean and spend approximately one year before spawning, although some males stay in freshwater for their entire life [@moritaLatitudinalVariationGrowth2010; @sahashiMigrationCostsDrive2013; @moritaTemperaturedependentVariationAlternative2014]. It has been shown that ocean-migrating adults of hatchery masu salmon show lower return rates to the spawning river [@sahashiWildGenesBoost2022], and such genetic effects may accumulate during the successive generations in captivity [@arakiGeneticEffectsCaptive2007]. Typically, masu salmon are reared in captivity for two to four generations. In light of the 70-year period of the extensive release program, it is conceivable that the "hatchery gene" has spread within the wild populations with measurable fitness declines. This effect may add to negative density dependence to influence community stability.

@@

It is noteworthy that the scale of the release program at the protected watersheds (annual average maximum = `r op(max(df_stock_mu$mean_stock), 2)` million fish) is comparable or even smaller when compared with those for other fishery resources [@laikreCompromisingGeneticDiversity2010; @kitadaEconomicEcologicalGenetic2018]. For example, 649.1 million fish are released annually to supplement the pink salmon stock at the Prince William Sound in Alaska, where wild populations seem to be severely compromised due to competition with hatchery fish [@amorosoMeasuringNetBiological2017]. Similarly, the large-scale release of Black sea bream has been conducted in Kagoshima Bay (Japan) since 1974 (the yearly-average of 0.64 million juveniles) with associated declines of wild stocks and genetic diversity [@kitadaRigorousMonitoringLargescale2019]. Although we do not know the carrying capacities of the recipient systems, it is clear that our results should not be viewed as an exceptional case. In support of this view, a meta-analysis revealed that only a few massive release programs in fisheries led to an increased abundance of the focal species [@arakiHatcheryStockingHelp2010]. Yet, none of those studies statistically quantified the community-level impact. Future studies addressing this knowledge gap are therefore desired to generalize our findings.

Two unique strengths in our dataset may have helped uncover the qualitative agreement between theory and empirical patterns. First, human activities are strictly regulated in the protected watersheds (**Figure S10**). Any form of exploitation, including angling, is prohibited in these areas. In addition, exclusive permission from the governer of Hokkaido is required to physically alter in-stream and riparian habitats. Therefore, unmeasured human influences should have minimal influences on the observed relationships. As such, we were able to confine potential confounding factors to natural environmental variation, which were properly accounted in our statistical model (see **Methods**). Second, the sampling method in this monitoring program (a combination of cast net and electrofishing) is carefully chosen to capture stream fishes with different microhabitat preference (e.g., water-column vs. bottom). Thus, our data is robust to potential sampling bias. Nevertheless, our results must be viewed with some caution: we cannot exclude the possibility of spurious correlations due to the inherent nature of correlative analysis and field research. Since an experimental approach is nearly impossible at this spatial scale, the application of novel causal inferences (e.g., convergent cross mapping) [@sugiharaDetectingCausalityComplex2012; @ushioFluctuatingInteractionNetwork2018; @suzukiDecomposingPredictabilityIdentify2022] may be a potential alternative to confirm the causal relationship between intentional release and community dynamics. Unfortunately, these methods were not applicable to our data because they require a longer and non-sparse time series to yield robust results.

@@

Despite the significant attention to the fate of captive-bred individuals [@arakiHatcheryStockingHelp2010; @snyderLimitationsCaptiveBreeding1996], current schemes rarely consider the self-regulation process of biodiversity. Our results suggest that ignorance of this critical process may erode the long-term persistence of the recipient community, likely impacting the stable delivery of ecosystem services [@cardinaleBiodiversityLossIts2012]. We anticipate that the detrimental community-level consequence is not rare, or even pervasive, because many release programs are designed to aid declining populations [@fischerAssessmentPublishedResults2000; @haagNorthAmericanFreshwater2012; @strayerEssayMakingMost2019; @hilbornEconomicPerformanceMarine1998]. In rural Spain, two million individuals of reared red-legged partridge, the most important game bird in this area, are introduced into the wild every year to overcome the regional decline of this species [@negroRAPDAnalysisDetection2001]. In the US, a nation-wide initiative exists to augment populations of freshwater mussels, which are rapidly disappearing over the past decades for enigmatic reasons [@haagNorthAmericanFreshwater2012]. The exact causes behind such population declines are often unknown or controversial, yet it is reasonable to assume that those habitats are no longer suitable and can support limited numbers of individuals (i.e., low carrying capacity). As long as this important theoretical condition of limited carrying capacity holds true, the phenomenon observed in our study streams may occur broadly across taxa and ecosystems.

While socioeconomic analysis is required to provide detailed guidance on release programs, it is clear that habitat conservation should be prioritized for the sustainability of the natural resources. Protected areas and environmental restoration are promising tools to conserve biodiversity, and a smart spatial design is integral to achieving successful conservation. For example, coordinated placement of conservation sites considering spatial biodiversity patterns is crucial in improving the ecological outcomes [@akasakaSmartProtectedArea2017; @teruiEmergentDualScaling2021; @koningNetworkGrassrootsReserves2020; @fontouraProtectingConnectivityPromotes2022]. Governance may also play a central role in enforcing environmental legislation, potentially determining the effectiveness of conservation investment [@amanoSuccessfulConservationGlobal2018]. These considerable potentials indicate that viable management options exist before blindly accepting intentional release. Without a comprehensive framework that appreciates the ecological integrity of natural communities, the intentional release will never be effective but impairs biodiversity.

@@

We subsequently analyzed a whole community model with 10 species using important parameter combinations identified in the two-species simulation: intrinsic growth of enhanced species ($r_1 =$ `r unique(list_param[[2]]$r1)`), average strength of interspecific competition ($\bar{\alpha}=$ `r unique(list_param[[2]]$alpha)`), carrying capacity ($K=$ `r unique(list_param[[2]]$k)`). We also varied relative fitness of captive-bred individuals ($f_R=$ `r unique(list_param[[2]]$phi)`) as this is a common interest in captive-breeding programs. Meanwhile, we fixed values of the following parameters: the number of species ($S=$ `r unique(list_param[[2]]$n_species)`), maximum intrinsic growth rate of unenhanced species ($r_{\text{max}}=$ `r unique(list_param[[2]]$r_max)`), and environmental stochasticity ($\sigma_{\varepsilon}=$ `r unique(list_param[[2]]$sd_env)`). We used $r_{\text{max}}=$ `r unique(list_param[[2]]$r_max)` because the intrinsic growth rate higher than this value was rarely observed in nature [@myersMaximumReproductiveRate1999]. This simulation setup resulted in `r nrow(list_param[[2]])` sets of parameter combinations.

As with the two-species model, we ran `r attr(list_param[[2]], "n_sim")` timesteps of community dynamics with `r max(list_sim[[2]]$n_rep)` values of release level $R$ ($0$ to $500$ with a constant interval) for each simulation scenario. In this simulation, we initialized the community by introducing five individuals of each species and repeated this seeding every ten timesteps to account for possible complex dynamics of a ten-species community. In addition, we defined a threshold density ($N_i = 0.01$) below which species are removed from the simulation (i.e., an absorbing condition) and are recorded as "extinct". The rest of the simulation procedure is identical to the two-species model. We summarized values of simulation parameters in **Table S**1.

@@

**Environmental data.** At each sampling site, we measured the following environmental variables as potential covariates: upstream watershed area (km^2^; a proxy for stream size), proportional land use in the upstream watershed (forest, urban, agriculture), local climates (annual mean air temperature [$^\circ C$] and cumulative precipitation [mm]), and ocean productivity (sea surface chlorophyll *a* concentration [mg m^-3^]). We used MERIT Hydro [@yamazakiMERITHydroHighresolution2019] to delineate the upstream watershed polygon for each sampling site. We estimated the proportion of forest, urban, and agriculture in each watershed polygon based on land use data in 2015 from Copernicus Global Land Service (100-m resolution) [@marcelbuchhornCopernicusGlobalLand2020]. Climate data at each sampling site were extracted from CHELSA version 1.2 [@kargerClimatologiesHighResolution2017; @kargerDataClimatologiesHigh2018]. We extracted annual data of chlorophyll *a* concentration (2002 -- 2019; resolution, 4.6 km^2^) from OceanColor [@seawifsmissionpageNasaOceanBiology2019] as a proxy for ocean productivity and calculated the average value within the 30-km radius of each river mouth. We used the following R packages to perform geospatial analysis: *sf* [@pebesmaSimpleFeaturesStandardized2018], *terra* [@hijmansTerraSpatialData2022], *exactextractr* [@bastonExactextractrFastExtraction2020], *stars* [@pebesmaStarsSpatiotemporalArrays2020], *whitebox* [@lindsayWhiteboxGATCase2016]*.*

@@

$\gamma'_{0}$ is the global intercept and $\gamma'_k$ is the regression coefficients of ocean productivity $\gamma'_{1,w}$ (chlorophyll *a* concentration; averaged for 2002 -- 2019) and standard deviation of elevation (SD elevation) within an entire watershed $\gamma'_{2,w}$. Ocean productivity was included because the majority of the observed species use marine habitats at a certain life stage (i.e., diadromous). SD elevation is a landscape-level variable that may dictate long-term flow dynamics. The parameter $\sigma_{\gamma}$ accounts for random variation among watersheds that the watershed-level predictors cannot capture.

>>>>

The intentional release, however, can have wider-ranging consequences than previously thought, as the impacts can propagate through a diversity of ecological interactions [@careyNativeInvadersChallenges2012]. This recognition has sparked a discussion of how the massive introduction of native species alters short-term ecosystem dynamics [@hasegawaAreHatcheryChum2018; @nelsonEcologicalImplicationsChanging2019; @cucheroussetAreDomesticatedFreshwater2020]. Yet, current debates overlook the fact that we have rarely assessed the community-wide impact in the long-term. Ecological theory suggests that the stable coexistence of competing species through density-dependent feedback underpins the emergent stability of ecological communities [@tilmanEcologicalConsequencesChanges1999; @carrollNicheFitnessDifferences2011a; @loreauDoesFunctionalRedundancy2004]. Intentional release may disrupt the sensitive balance of species interactions because it introduces unnaturally high numbers of individuals into the wild [@laikreCompromisingGeneticDiversity2010; @careyNativeInvadersChallenges2012; @kitadaEconomicEcologicalGenetic2018]. Hence, this form of species management may intervene in the ecological process that allows competing species to coexist, ultimately degrading the long-term community stability. Evidence for this hypothesis is lacking, however.

@@

The intentional release had little or a stabilizing influence on community dynamics when carrying capacity was sufficiently large ($K=$ `r max(list_param[[2]]$k)`; **Figures S7 -- S10**). In particular, intentional release increased the enhanced species with a low population growth rate ($r_1=$ `r min(list_param[[2]]$r1)`; **Figure S7**), suggesting that weak intraspecific competition within the enhanced species (= $r_1 K^{-1}$) is needed for intentional release to be effective. The weak-competition scenario is likely in the reintroduction of extirpated species or long-lived endangered species. In fact, some of the best evidence for successful intentional release comes from conservation programs of such species [@deguchiTranslocationHandrearingResult2017; @jonesRestorationMauritiusKestrel1995; @okahisaEvaluationOngoingCrested2022; @yackulicAssessingPopulationImpacts2021]. In the Sado island (Japan), for example, the once-extirpated Crested Ibis *Nipponia nippon* showed exponential growth of the population since the initial reintroduction of ten captive-bred individuals in 2008 [@okahisaEvaluationOngoingCrested2022]. Similarly, translocations of Humpback chub, a federally-listed fish species in the US, seem highly cost-effective in enhancing their tributary populations in the Little Colorado River [@yackulicAssessingPopulationImpacts2021]. However, the preponderance of unsuccessful reintroduction in conservation implies that the theoretical requirements for successful intentional release are not always met [@fischerAssessmentPublishedResults2000; @haagNorthAmericanFreshwater2012; @strayerEssayMakingMost2019]. Indeed, non-negligible numbers of projects seem to release captive-bred individuals into unsuitable habitats with compromised carrying capacities [@fischerAssessmentPublishedResults2000; @haagNorthAmericanFreshwater2012]. Our analysis suggests that such programs could rather impair biodiversity without noticeable demographic benefit to the enhanced species. Pre-release examination and restoration of environmental capacity may be key to successful release programs with minimal impacts on other community members.

@@

To demonstrate the relevance of our general theory to natural systems, we assessed the potential impacts of the intentional release of masu salmon (**Figure 1D**) on the long-term stability of stream fish communities in Hokkaido, Japan. In the protected watersheds (all separated by the ocean; **Figure 1C**), a long-term program exists to monitor stream fish communities along with the official release records. The release of masu salmon began in the 1950s; the release numbers vary due mainly to logistical reasons, while several of the watersheds are not subject to intentional release to preserve regional populations. This resulted in the average annual release ranging from `r round(min(df_stock_mu$mean_stock), 2)` (no release) to `r round(max(df_stock_mu$mean_stock), 2)` million fish across watersheds during 1999 -- 2019. Most release occurs in spring near fish survey locations, after which salmon fry stays in freshwater for at least one year with other stream fishes (see **Figure S16** for a co-occurrence matrix in our dataset). Therefore, the study system sets the stage for a "natural experiment" to test our theoretical predictions. We used the data from 1999 to 2019 at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` independent watersheds (see **Methods** for selection criteria). Using hierarchical Bayesian models, we quantified the effect of intentional release on community dynamics while accounting for the potential effects of climates and local abiotic factors.

@@

The reduced fitness of hatchery masu salmon may also play a role in the observed response. Like other salmonids, masu salmon exhibits a life history of "partial migration"; in our study region, the majority of individuals migrate to the ocean and spend approximately one year before spawning, although some males stay in freshwater for their entire life [@moritaLatitudinalVariationGrowth2010; @sahashiMigrationCostsDrive2013; @moritaTemperaturedependentVariationAlternative2014]. It has been shown that ocean-migrating adults of hatchery masu salmon show lower return rates to the spawning river [@sahashiWildGenesBoost2022], and such genetic effects may accumulate during successive generations in captivity [@arakiGeneticEffectsCaptive2007]. Typically, masu salmon are reared in captivity for two to four generations. In light of the 70-year period of the extensive release program, it is conceivable that the "hatchery gene" has spread within the wild populations with measurable fitness declines. This effect may add to negative density dependence to influence community stability.

@@

It is noteworthy that the scale of the release program at the protected watersheds (annual average maximum = `r op(max(df_stock_mu$mean_stock), 2)` million fish) is comparable or even smaller when compared with those for other fishery resources [@laikreCompromisingGeneticDiversity2010; @kitadaEconomicEcologicalGenetic2018]. For example, 649.1 million fish are released annually to supplement the pink salmon stock at the Prince William Sound in Alaska, where wild populations seem to be severely compromised due to competition with hatchery fish [@amorosoMeasuringNetBiological2017]. Similarly, the large-scale release of Black sea bream has been conducted in Kagoshima Bay (Japan) since 1974 (a yearly average of 0.64 million juveniles) with associated declines of wild stocks and genetic diversity [@kitadaRigorousMonitoringLargescale2019]. Although we do not know the carrying capacities of the recipient systems, it is clear that our results should not be viewed as an exceptional case. In support of this view, a meta-analysis revealed that only a few massive release programs in fisheries led to an increased abundance of the focal species [@arakiHatcheryStockingHelp2010]. Yet, none of those studies statistically quantified the community-level impact. Future studies addressing this knowledge gap are therefore desired to generalize our findings.

Two unique strengths in our dataset may have helped uncover the qualitative agreement between theory and empirical patterns. First, human activities are strictly regulated in the protected watersheds (**Figure S10**). Any form of exploitation, including angling, is prohibited in these areas. In addition, exclusive permission from the governor of Hokkaido is required to physically alter in-stream and riparian habitats. Therefore, unmeasured human influences should have minimal influences on the observed relationships. As such, we were able to confine potential confounding factors to natural environmental variation, which were properly accounted for in our statistical model (see **Methods**). Second, the sampling method in this monitoring program (a combination of cast net and electrofishing) is carefully chosen to capture stream fishes with different microhabitat preferences (e.g., water-column vs. bottom). Thus, our data is robust to potential sampling bias. Nevertheless, our results must be viewed with some caution: we cannot exclude the possibility of spurious correlations due to the inherent nature of correlative analysis and field research. Since an experimental approach is nearly impossible at this spatial scale, the application of novel causal inferences (e.g., convergent cross mapping) [@sugiharaDetectingCausalityComplex2012; @ushioFluctuatingInteractionNetwork2018; @suzukiDecomposingPredictabilityIdentify2022] may be a potential alternative to confirm the causal relationship between intentional release and community dynamics. Unfortunately, these methods were not applicable to our data because they require a longer and non-sparse time series to yield robust results.

@@

Despite the significant attention to the fate of captive-bred individuals [@arakiHatcheryStockingHelp2010; @snyderLimitationsCaptiveBreeding1996], current schemes rarely consider the self-regulation process of biodiversity. Our results suggest that ignorance of this critical process may erode the long-term persistence of the recipient community, likely impacting the stable delivery of ecosystem services [@cardinaleBiodiversityLossIts2012]. We anticipate that the detrimental community-level consequence is not rare, or even pervasive, because many release programs are designed to aid declining populations [@fischerAssessmentPublishedResults2000; @haagNorthAmericanFreshwater2012; @strayerEssayMakingMost2019; @hilbornEconomicPerformanceMarine1998]. In rural Spain, two million individuals of reared red-legged partridge, the most important game bird in this area, are introduced into the wild every year to overcome the regional decline of this species [@negroRAPDAnalysisDetection2001]. In the US, a nationwide initiative exists to augment populations of freshwater mussels, which have been rapidly disappearing over the past decades for enigmatic reasons [@haagNorthAmericanFreshwater2012]. The exact causes behind such population declines are often unknown or controversial, yet it is reasonable to assume that those habitats are no longer suitable and can support limited numbers of individuals (i.e., low carrying capacity). As long as this important theoretical condition of limited carrying capacity holds true, the phenomenon observed in our study streams may occur broadly across taxa and ecosystems.

While socioeconomic analysis is required to provide detailed guidance on release programs, it is clear that habitat conservation should be prioritized for the sustainability of natural resources. Protected areas and environmental restoration are promising tools to conserve biodiversity, and a smart spatial design is integral to achieving successful conservation. For example, coordinated placement of conservation sites considering spatial biodiversity patterns is crucial in improving the ecological outcomes [@akasakaSmartProtectedArea2017; @teruiEmergentDualScaling2021; @koningNetworkGrassrootsReserves2020; @fontouraProtectingConnectivityPromotes2022]. Governance may also play a central role in enforcing environmental legislation, potentially determining the effectiveness of conservation investment [@amanoSuccessfulConservationGlobal2018]. These considerable potentials indicate that viable management options exist before blindly accepting intentional release. Without a comprehensive framework that appreciates the ecological integrity of natural communities, the intentional release will never be effective but impairs biodiversity.

@@

We subsequently analyzed a whole community model with 10 species using important parameter combinations identified in the two-species simulation: intrinsic growth of enhanced species ($r_1 =$ `r unique(list_param[[2]]$r1)`), average strength of interspecific competition ($\bar{\alpha}=$ `r unique(list_param[[2]]$alpha)`), carrying capacity ($K=$ `r unique(list_param[[2]]$k)`). We also varied the relative fitness of captive-bred individuals ($f_R=$ `r unique(list_param[[2]]$phi)`) as this is a common interest in captive-breeding programs. Meanwhile, we fixed values of the following parameters: the number of species ($S=$ `r unique(list_param[[2]]$n_species)`), maximum intrinsic growth rate of unenhanced species ($r_{\text{max}}=$ `r unique(list_param[[2]]$r_max)`), and environmental stochasticity ($\sigma_{\varepsilon}=$ `r unique(list_param[[2]]$sd_env)`). We used $r_{\text{max}}=$ `r unique(list_param[[2]]$r_max)` because the intrinsic growth rate higher than this value was rarely observed in nature [@myersMaximumReproductiveRate1999]. This simulation setup resulted in `r nrow(list_param[[2]])` sets of parameter combinations.

As with the two-species model, we ran `r attr(list_param[[2]], "n_sim")` timesteps of community dynamics with `r max(list_sim[[2]]$n_rep)` values of release level $R$ ($0$ to $500$ with a constant interval) for each simulation scenario. In this simulation, we initialized the community by introducing five individuals of each species and repeated this seeding every ten timesteps to account for possible complex dynamics of a ten-species community. In addition, we defined a threshold density ($N_i = 0.01$) below which species are removed from the simulation (i.e., an absorbing condition) and are recorded as "extinct." The rest of the simulation procedure is identical to the two-species model. We summarized the values of simulation parameters in **Table S**1.

@@

**Environmental data.** At each sampling site, we measured the following environmental variables as potential covariates: upstream watershed area (km^2^; a proxy for stream size), proportional land use in the upstream watershed (forest, urban, agriculture), local climates (annual mean air temperature [$^\circ C$] and cumulative precipitation [mm]), and ocean productivity (sea surface chlorophyll *a* concentration [mg m^-3^]). We used MERIT Hydro [@yamazakiMERITHydroHighresolution2019] to delineate the upstream watershed polygon for each sampling site. We estimated the proportion of forest, urban, and agriculture in each watershed polygon based on land use data in 2015 from Copernicus Global Land Service (100-m resolution) [@marcelbuchhornCopernicusGlobalLand2020]. Climate data at each sampling site were extracted from CHELSA version 1.2 [@kargerClimatologiesHighResolution2017; @kargerDataClimatologiesHigh2018]. We extracted annual data of chlorophyll *a* concentration (2002 -- 2019; resolution, 4.6 km^2^) from OceanColor [@seawifsmissionpageNasaOceanBiology2019] as a proxy for ocean productivity and calculated the average value within the 30-km radius of each river mouth. We used the following R packages to perform the geospatial analysis: *sf* [@pebesmaSimpleFeaturesStandardized2018], *terra* [@hijmansTerraSpatialData2022], *exactextractr* [@bastonExactextractrFastExtraction2020], *stars* [@pebesmaStarsSpatiotemporalArrays2020], *whitebox* [@lindsayWhiteboxGATCase2016]*.*

@@

$\gamma'_{0}$ is the global intercept, and $\gamma'_k$ is the regression coefficients of ocean productivity $\gamma'_{1,w}$ (chlorophyll *a* concentration; averaged for 2002 -- 2019) and standard deviation of elevation (SD elevation) within an entire watershed $\gamma'_{2,w}$. Ocean productivity was included because the majority of the observed species use marine habitats at a certain life stage (i.e., diadromous). SD elevation is a landscape-level variable that may dictate long-term flow dynamics. The parameter $\sigma_{\gamma}$ accounts for random variation among watersheds that the watershed-level predictors cannot capture.

### 2022-12-24 rmd/reply_r2.Rmd
edit: grammar

This is a revision of a manuscript: "2022­18044 *Intentional release of native species undermines ecological stability.*" Thank you for allowing us to revise our manuscript. We have refined our analysis and text in light of comments from the reviewer 3. We hope the manuscript is suitable for publication in PNAS.

@@

> We appreciate your recommendation. We believe our unclear writing has caused a confusion -- please let us clarify.
>
> First, the sampling method in the protected watersheds are consistent across all sites and years, so there is no need to include the sampling method as a control factor in the statistical model (clarified in Methods). Further, the sampling method (a combination of cast net and electrofishing) was carefully chosen to catch both water-column and benthic fish species effectively (clarified and mentioned in Discussion; L. 227 --). Therefore, we believe our data are robust to sampling bias.
>
> Second, we appreciate reviewer's comment on irregular sampling interval. In the revised analysis, we have included the number of observation years as an additional covariate to address reviewer's concern. The results were qualitatively similar. Please see also our response to reviewer 3.
>
> Overall, we confirmed that our results were robust to concerns raised by reviewer 3.

@@

> Thank you. This is perhaps because of our unclear writing. At all sites, a combination of electrofishing and cast net was used to capture both benthic and water-column species effectively. We have clarified this in the revised MS (L 333 --). In addition, we have added some text to clarify that the sampling has constant sampling effort per unit area (see **Supplementary text**). Therefore, our analysis is robust to this issue.

@@

> The secondary analysis at sites with no missing data would be insightful for sure. However, it introduces the issue of sample size. To address reviewer's concern more appropriately, we included "the number of observation years" as a covariate in the regression model. This approach is suitable because it keeps the sample size as original while accounting for potential influences of observation intervals. The results were qualitatively similar, confirming the robustness of our results.

@@

> Thank you for your careful reading. However, this data point is not identified as an outlier; thus, there is no statistical justification for removing it from analysis. Although the figure was shown in an ordinary scale, the analysis was carried out in a log-scale (see Methods). When we applied the Grubb's test to the log-transformed CV, the p-value was 0.176, indicating that our results were not strongly influenced by the highest value of CV (see R codes below). Also, we have confirmed that our results were robust even if we used robust regression with the MM method, which accounts for potential outliers in both response (log CV) and predictor variables (effective release). We hope this ameliorates reviewer's concern.

@@

> Thank you for this comment. We agree with this opinion. However, we believe our analysis has already accounted for this aspect. The main response variable in our analysis (CV) is the aggregate measure of all species present in the community, namely: $CV = \frac{\sqrt{\sum \sigma^2_i + \sum \sum Cov_{ij}}}{\sum \mu_i}$ ($\sigma_i$ is the SD for species $i$). Therefore, the point raised by the reviewer is already accounted in our model, albeit implicitly. Also, we wanted to remind the reviewer that our results indicated that the community SD was not influenced by intentional release. Although we cannot exclude the possible importance of relative community composition, our data suggest that it has a minimal influence on the dynamics (at least in our system).

@@

> Some of the watersheds (e.g. Shimonaefutoro) do not receive stocking for the purpose of regional population conservation. The rest of variation across watersheds are due largely to logistical reasons (e.g., accessibility). We have briefly mentioned this in the revised MS (L. 158 --).

@@

> We are glad that the reviewer caught this! Yes, the reviewer is right - different programes release plants, insects, birds, fish etc. We have revised the text.

@@

> Thank you for the important suggestion. We agree that different types of interactions may be important to understand ecosystem-wide impacts of intentional release. We have clarified this point in the revised manuscript. In the meantime, we believe our research is unique and significant in that we have quantified "long-term" impact at the community level. As the reviewer suggested, there are some discussion on the community-level impact of intentional release (very few though). However, none of them evaluated the long-term impact. We have improved the description about the knowledge gap addressed in this study (L51 --)

>>>>

This is a revision of a manuscript: "2022­18044 *Intentional release of native species undermines ecological stability.*" Thank you for allowing us to revise our manuscript. We have refined our analysis and text in light of comments from reviewer 3. We hope the manuscript is suitable for publication in PNAS.

@@

> We appreciate your recommendation. Our unclear writing has caused confusion -- please let us clarify.
>
> First, the sampling method in the protected watersheds is consistent across all sites and years, so there is no need to include the sampling method as a controlling factor in the statistical model (clarified in Methods). Further, the sampling method (a combination of cast net and electrofishing) was carefully chosen to catch both water-column and benthic fish species effectively (clarified and mentioned in Discussion; L. 227 --). Therefore, our data are robust to sampling bias.
>
> Second, we appreciate the reviewer's comment on irregular sampling intervals. In the revised analysis, we have included the number of observation years as an additional covariate to address the reviewer's concern. The results were qualitatively similar. Please see also our response to reviewer 3.
>
> Overall, we confirmed that our results were robust to concerns raised by reviewer 3.

@@

> Thank you. This is perhaps because of our unclear writing. At all sites, a combination of electrofishing and cast net was used to capture both benthic and water-column species effectively. We have clarified this in the revised MS (L 333 --). In addition, we have added some text to explain that the sampling has constant sampling effort per unit area (see **Supplementary text**). Therefore, our analysis is robust to this issue.

@@

> The secondary analysis at sites with no missing data would be insightful for sure. However, it introduces the issue of sample size. To address the reviewer's concern more appropriately, we included "the number of observation years" as a covariate in the regression model. This approach is suitable because it keeps the sample size as original while accounting for potential influences of observation intervals. The results were qualitatively similar, confirming the robustness of our results.

@@

> Thank you for your careful reading. However, this data point is not identified as an outlier; thus, there is no statistical justification for removing it from the analysis. Although the figure was shown on an ordinary scale, the analysis was carried out on a log-scale (see Methods). When we applied the Grubb's test to the log-transformed CV, the p-value was 0.176, indicating that our results were not strongly influenced by the highest value of CV (see R codes below). Also, we have confirmed that our results were robust even if we used robust regression with the MM method, which accounts for potential outliers in both response (log CV) and predictor variables (effective release). We hope this ameliorates the reviewer's concern.

@@

> Thank you for this comment. We agree with this opinion. However, we believe our analysis has already accounted for this aspect. The main response variable in our analysis (CV) is the aggregate measure of all species present in the community, namely: $CV = \frac{\sqrt{\sum \sigma^2_i + \sum \sum Cov_{ij}}}{\sum \mu_i}$ ($\sigma_i$ is the SD for species $i$). Therefore, the point raised by the reviewer is already accounted for in our model, albeit implicitly. Also, we wanted to remind the reviewer that our results indicated that the community SD was not influenced by intentional release. Although we cannot exclude the possible importance of relative community composition, our data suggest that it has a minimal influence on the dynamics (at least in our system).

@@

> Some of the watersheds (e.g. Shimonaefutoro) do not receive stocking for the purpose of regional population conservation. The rest of the variation across watersheds is due largely to logistical reasons (e.g., accessibility). We have briefly mentioned this in the revised MS (L. 158 --).

@@

> We are glad that the reviewer caught this! Yes, the reviewer is right - different programs release plants, insects, birds, fish etc. We have revised the text.

@@

> Thank you for the important suggestion. We agree that different types of interactions may be important to understand the ecosystem-wide impacts of intentional release. We have clarified this point in the revised manuscript. In the meantime, we believe our research is unique and significant in that we have quantified "long-term" impact at the community level. As the reviewer suggested, there is some discussion about the community-level effects of intentional release (very few, though). However, none of them evaluated the long-term impact. We have improved the description of the knowledge gap addressed in this study (L51 --)
